Tables

### 2020-03-04 manuscript/figures.Rmd
Added additional Missing crown and crown transparency descriptors to COD response surface plots. Corrected caption
altered methods to reflect use of total height and lower crown height in DAI response surfaces. Lower bound of total height now upper bound of lower crown height to avoid impossible situations
corrections to tables,figures and supplementary

```{r decline_index_plot,fig.cap='Decline indexes for all 174 trees. The chosen group categories were selected in the field prior to data collection. AOD = acute oak decline; COD = chronic oak decline. Remisson tress were those that were known to have had active bleeds within the previous 3 years.'}
loadd(decline_indexes_plot)

@@

```{r descriptor_contributions, fig.height = 6,fig.cap = 'Descriptor mean decrease in accuracy importance scores from the random forest models $M_{PDI}$ and $M_{DAI}$ for relative contributions to the decline index measures. Descriptors are ordered by descending percentage increase in mean squared error (MSE) and therefore from highest contribution to lowest contribution to the given decline index.'}
loadd(descriptor_contribution_plots)

@@

```{r DAI_response_surfaces,fig.height = 8,fig.cap='DAI response surfaces from $M_{DAI}$ for simulated values of key contributing descriptors for example cases. The neutral case is a tree that can be neither distinguished as AOD or COD. All cases have PDI values > 0.5.'}
loadd(DAI_response_surfaces)

>>>>

```{r decline_index_plot,fig.cap='Decline indexes for all 174 surveyed trees. The chosen group categories were selected in the field prior to data collection. AOD = acute oak decline; COD = chronic oak decline. Remisson tress were those that were known to have had active bleeds within the previous 3 years.'}
loadd(decline_indexes_plot)

@@

```{r descriptor_contributions, fig.height = 6,fig.cap = 'Descriptor importance scores from the random forest models $M_{PDI}$ and $M_{DAI}$ for relative contributions to the decline index measures. Descriptors are ordered by descending percentage increase in mean squared error (MSE) and therefore from highest contribution to lowest contribution to the given decline index.'}
loadd(descriptor_contribution_plots)

@@

```{r DAI_response_surfaces,fig.height = 8,fig.cap='DAI response surfaces from $M_{DAI}$ for simulated values of key contributing descriptors for example cases. The neutral case is a tree that can be neither distinguished as AOD or COD. All cases have PDI values > 0.5. The values of additional descriptors related to bleed prevalence and relative stature/crown condition are shown for the AOD and COD example cases respectively.'}
loadd(DAI_response_surfaces)

### 2020-03-04 manuscript/supplementary.Rmd
corrections to tables,figures and supplementary

site_correction_factors %>%
  mutate_if(is.double,signif,digits = 3) %>%
  kable(format = 'latex',booktabs = TRUE,caption = 'Descriptor adjustment factors at each site.') %>%
  collapse_rows(columns = 1,latex_hline = "major", valign = "middle")
```

>>>>

site_correction_factors %>%
  rename(Adjustment = Correction) %>%
  mutate_if(is.double,signif,digits = 3) %>%
  kable(format = 'latex',booktabs = TRUE,caption = 'Descriptor adjustment factors at each site.') %>%
  collapse_rows(columns = 1,latex_hline = "major", valign = "middle")
```

### 2020-03-04 manuscript/tables.Rmd
corrections to tables,figures and supplementary

PDI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results for oak decline severity cases in the PDI index model. Top four important descriptors show. Descriptors ordered by descending absolute weight within each case.') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

@@

DAI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results of oak decline type and severity in the DAI index model. Top four important descriptors shown. Descriptors ordered by descending absolute weight within each case.') %>%
  column_spec(5,width = '4cm') %>%
  collapse_rows(columns = 1:4, latex_hline = "custom", valign = "middle",custom_latex_hline = 1:4)
```

>>>>

PDI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results for oak decline severity cases in the PDI index model $M_{PDI}$. Top four important descriptors show. Descriptors ordered by descending absolute weight within each case.') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

@@

DAI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results of oak decline type and severity in the DAI index model $M_{DAI}$. Top four important descriptors shown. Descriptors ordered by descending absolute weight within each case.') %>%
  column_spec(5,width = '4cm') %>%
  collapse_rows(columns = 1:4, latex_hline = "custom", valign = "middle",custom_latex_hline = 1:4)
```
